\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-04-23 paper.qmd
Add offset def

Number of bins is set by fixing $b_1$, which determines the binwidth and breaks on $x_1$, is calculated as

@@

The computed binwidth then determines the number of vertical bins, $b_2$, and vertical binwidth, which are computed based on $r_2$, and the height/width ratio of a regular hexagon, $\frac{2}{\sqrt{3}}$ as

>>>>

Number of bins is set by fixing $b_1$, which determines the binwidth accounting the offset $q_1$ and breaks on $x_1$, is calculated as

@@

The computed binwidth then determines the number of vertical bins, $b_2$, and vertical binwidth, which are computed based on $r_2$, the offset $q_2$, and the height/width ratio of a regular hexagon, $\frac{2}{\sqrt{3}}$ as

### 2024-04-23 paper.tex
Add offset def

Number of bins is set by fixing \(b_1\), which determines the binwidth
and breaks on \(x_1\), is calculated as

@@

The computed binwidth then determines the number of vertical bins,
\(b_2\), and vertical binwidth, which are computed based on \(r_2\), and
the height/width ratio of a regular hexagon, \(\frac{2}{\sqrt{3}}\) as

>>>>

Number of bins is set by fixing \(b_1\), which determines the binwidth
accounting the offset \(q_1\) and breaks on \(x_1\), is calculated as

@@

The computed binwidth then determines the number of vertical bins,
\(b_2\), and vertical binwidth, which are computed based on \(r_2\), the
offset \(q_2\), and the height/width ratio of a regular hexagon,
\(\frac{2}{\sqrt{3}}\) as
